---
title: "Class_06"
author: "Scarlett F Haynes"
date: "2026-09-21"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    number_sections: TRUE
    code_download: TRUE
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Quick Loading of data from Assignment 04

```{r hw04}
con = DBI::dbConnect(RSQLite::SQLite(), "../data/midwest_airbnb.db")
listings = DBI::dbReadTable(con, "listings")
```

# Kahoot 02
```{r kahoot 2}
run = readr::read_csv(
  "https://isa401-find-your-seat.vercel.app/api/export?section=A&run=13")
dplyr::glimpse(run)
```
## 1. campus is a named list and Farmer is one of its elements. What does campus["Farmer"] give you?
A. An error
B. A shorter list ✅
C. A 10 row data frame
D. A shorter vector  

Correct Answer: A shorter list


## 2. Why did we download occupation.xlsx in the browser instead of reading it from its web address?
A. Excel files are binary and R cannot read them
B. To practice File > Save
C. read_excel() needs a file on disk ✅
D. The file was too large for R  

Correct Answer: read_excel() needs a file on disk

## 3. In the following code, what does skip = 1 do?
read_excel("../data/occupation.xlsx", sheet = "Table 1.3", skip = 1, n_max = 3)
A. Drops the footnote rows
B. Skips the title row above the header ✅
C. Skips the first sheet
D. Reads only one row  

Correct Answer: Skips the title row above the header


## 4. Your markdown lives in markdowns/ and the workbook is in data/. Which path works when you click Knit?
A. "../data/occupation.xlsx" ✅
B. "occupation.xlsx"
C. "data/occupation.xlsx"
D. "isa401/data/occupation.xlsx"  

Correct Answer: "../data/occupation.xlsx"


## 5. fromJSON() on the Cincinnati crash file returned a data frame where every column was character. Why?
A. glimpse() converts columns to character
B. The city publishes no numbers
C. fromJSON() always returns character columns
D. The file quotes every value, so R stores them as text ✅

Correct Answer: The file quotes every value, so R stores them as text


## 6. In the Heist, Stage 1 was a CSV file and Stage 2 was JSON. Which functions imported them?
A. read_csv() then fromJSON() ✅
B. read_csv and then read_json()
C. dbReadTable() for both
D. read_excel() for both  

Correct Answer: read_csv() then fromJSON()
